Manuscript for foodborne-outbreak Project

### 2023-02-24 products/manuscript/Manuscript.qmd
Update Manuscript.qmd

## Full Analysis

*Use one or several suitable statistical/machine learning methods to analyze your data and to produce meaningful figures, tables, etc. This might again be code that is best placed in one or several separate R scripts that need to be well documented. You want the code to produce figures and data ready for display as tables, and save those. Then you load them here.*

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","resulttable2.rds"))
knitr::kable(resulttable2)
```

@@

*Summarize what you did, what you found and what it means.*

@@

*Discuss what you perceive as strengths and limitations of your analysis.*

@@

*What are the main take-home messages?*

*Include citations in your Rmd file using bibtex, the list of references will automatically be placed at the end*

This paper [@leek2015] discusses types of analyses.

These papers [@mckay2020; @mckay2020a] are good examples of papers published using a fully reproducible setup similar to the one shown in this template.

Note that this cited reference will show up at the end of the document, the reference formatting is determined by the CSL file specified in the YAML header.
Many more style files for almost any journal [are available](https://www.zotero.org/styles).
You also specify the location of your bibtex reference file in the YAML.
You can call your reference file anything you like, I just used the generic word `references.bib` but giving it a more descriptive name is probably better.

>>>>

## Full Analysis (Machine Learning)

@@

@@

@@
